---
title: "Week 1 Exercise Part B"
author: "Greta Bordin"
format: html
editor: visual
---

### Sampling 100 values form a negative binomial distribution

In order to sample the desired data points it is possible to use the random generation option for the negative binomial distribution , *rnbinom* , with alternative parametrisation via *mean* as explained [here](https://stat.ethz.ch/R-manual/R-devel/library/stats/html/NegBinomial.html).

As in such parametrisation the variance is equal to *mu +mu^2^/ size* , and the task asks for the variance to be equal to *mu+mu^2^\*dispersion*, I am setting the *size* parameter to the inverse of the required *dispersion* = 2 (i.e 0.5).

```{r}
set.seed(123)
x <- rnbinom(100, mu = 10, size = 0.5)
x
```

The mean and variance of the above data points can be computed with:

```{r}
mean(x)
var(x)
```

Resulting in a mean of 9.36 and a variance of 140.7176.

### Plotting the sampled values as linear and log(x+1)-scale histograms

Binning options are tailored to each plot for better visualisation:

```{r}
h1 <- hist(x, breaks ='FD', plot = TRUE)
```

```{r}
h2 <- hist(log(x+1), plot = TRUE) 
```
